### 2023-10-13 ms.qmd
Updates

# Load data
	data  <-  read.csv("./output/data/data_activity.csv")
```

@@

@fig-fig1

>>>>

@@

# Load packages
pacman::p_load(tidyverse, flextable, brms, ggplot2)

# Load data
	data  <-  read.csv("./data/Learning.csv")
```

```{r, dataclean}
#| label: dataclean
#| echo: false
#| warning: false

# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)

data_associative <- data %>%
  group_by(lizard_id) %>%
  mutate(
    trial_associative = ifelse(!is.na(trial_associative), min(trial_associative, na.rm = TRUE), NA),
    trial_associative = trial_associative - min(trial_associative, na.rm = TRUE) + 1
  ) %>%
  ungroup()

# Split data
deli <- data_associative %>% filter (species == "delicata")
guich <- data_associative %>% filter (species == "guichenoti")
